---
title: "MICR 490 Homework 8"
output: github_document
---

``` {r}
library(tidyverse)
library(dplyr)
```


##Lists, data frames, and vectors

Creating the list
``` {r}
the_list <- list(the_data_frame = mtcars,
                 d_f_2 = USArrests,
                 the_vector = letters)
```

Accessing the first element by $ sign
```{r}
the_list $the_data_frame
```
Accessing the second element by number
```{r}
the_list[[2]]
```
Accessing the third element by name
```{r}
the_list["the_vector"]
```


Accessing the mpg column by name
```{r}
mtcars["mpg"]
```

Accessing the mpg column by $ sign
```{r}
mtcars$mpg
```


Creating the new column for Displacement per Cylinder by accessing each column individually, naming them each, then dividing them to create new column.  
Glimpse to see if it worked correctly
```{r}
disp <- mtcars$disp
cyl <- mtcars$cyl
disp_cyl = (disp/cyl)
mtcars$displacementpercylinder=disp_cyl
glimpse(mtcars)
```


Created new row mpg/disp called mpg.disp
```{r}
mpg_disp <- mutate(mtcars, mpg.disp= mpg*disp)
glimpse(mpg_disp)
```

Showing the single column of my mpg.disp data, tidyverse functions return data frames
```{r}
select(mpg_disp,mpg.disp)
```
``` {r}
num <- c(9,8,7,6)
as.factor(num)
```


``` {r}
as.numeric(num)
```

As a factor, the vector also shows levels and it arranges the numbers in numerical order. as a numeric vector, it only displays the numbers as I wrote them.

## Exploratory Data Analysis

I decided to use the airports data from the nyc flights data set
```{r}
library(nycflights13)
airports <- nycflights13::airports
glimpse(airports)
```

I created vectors from the Nycflights airports data set with just the airport names and the time zone for the airports
```{r}
nameports <- airports["name"]
timeports <- airports["tzone"]
```

Created a data frame with just the airport names and their time zones. 
```{r}
Nametime.data <- data.frame(nameports,timeports)
```

Showing the data in its own data frame
```{r}
glimpse(Nametime.data)
```

Created a table of the data
```{r}
table1 <- print.data.frame(Nametime.data)
```